---
title: "ABR6xBD21 Summary"
author: "Nathan Hughes"
date: "2 August 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html") 

# load libraries
library(stats)
library(plyr)
library(dplyr)
library(purrr)
library(readr)
library(ggplot2)
library(scales)
library(plotrix)
library(qtl)
library(knitr)
library(xtable)
library(GGally)
library(reshape2)
library(png)
library(ggfortify)

setwd('c:/Users/Nathan/Google Drive')

# example of grain phenotypes
img <- readPNG('GenSoc/Pretty Pictures/labwheat.png')

# load data
phendata = read_tsv('GenSoc/Data/Phenotypic Data/Compiled Data/medianRILs.tsv')
phendata$median_z <- NULL

abr6 = read_tsv('GenSoc/Data/Phenotypic Data/Compiled Data/abr6.tsv')
bd21 = read_tsv('GenSoc/Data/Phenotypic Data/Compiled Data/bd21.tsv')

# load qtl plotting functions 
source('GenSoc/QTL Mapping/Code/qtlplotter.R')

# load QTL
qtl = read.cross(format="qtlcart", 
                 file="GenSoc/Data/Genetic Map/More phens Map/qtlcart.cro",
                 mapfile="GenSoc/Data/Genetic Map/More phens Map/qtlcart.map")

qtl <- calc.genoprob(qtl, error.prob = 0.001)
```

## Phenotypic Data 
For clarification of Phenotypic discriptions, this is a labeled wheat grain 

```{r}
grid::grid.raster(img)
```


\clearpage

```{r, fig.width=10, fig.height=10}

ggcorr(bd21[, c('length','width','depth','circularity', 'volume','crease_depth',
                'surface_area', 'geometry_ratio')], 
       hjust = 0.6, label = TRUE, label_size = 4, size = 4 ) +
  annotate("Text", x = 3.5, y = 7, label = "Correlation of Median phenotypes\n of BD21") 

ggsave('bd21.png', plot = last_plot())

```

\clearpage

```{r, fig.width=10, fig.height=10}

ggcorr(abr6[, c('length','width','depth','circularity', 'volume','crease_depth', 
                'surface_area', 'geometry_ratio')],
       hjust = 0.6, label = TRUE, label_size = 4, size = 4 ) + 
  annotate("Text", x = 3.5, y = 7, label = "Correlation of Median phenotypes\n of ABR6") 

ggsave('abr6.png', plot = last_plot())

```

\clearpage

```{r, fig.width=10, fig.height=10}

ggcorr(phendata[, 2:9], hjust = 0.6, label = TRUE, label_size = 4, size = 4 ) +
  annotate("Text", x = 3.5, y = 7, 
           label = "Correlation of Median phenotypes\n of F8 Population") 

ggsave('cross-corr.png', plot = last_plot())

```

\clearpage

## Phenotypic Data (Cross Distributions)
```{r}
colnames(phendata) <- substring(colnames(phendata), 8)
d <- melt(phendata[,c('length','width','depth','circularity', 'volume','crease_depth', 
                      'surface_area', 'geometry_ratio')], id.vars = NULL)
ggplot(d,aes(x = value)) + 
    facet_wrap(~variable,scales = "free_x") + 
    geom_histogram(bins = 15, col = "black")

ggsave('hist.png', plot = last_plot())

```

\clearpage

## PCA of Phenotypes

```{r}

d <- phendata[,c('length','width','depth','circularity', 'volume','crease_depth', 
                      'surface_area')]


pcr <- prcomp(d)
autoplot(pcr)

ggsave('pca.png', plot = last_plot())

```

##  Genotypic Data 

```{r}
png('geno-est-map.png')
plot(est.map(qtl))
dev.off()
```

```{r}
png('geno-image.png')
geno.image(qtl)
dev.off()
```

- Few missing readings (white spots)
- Mostly complete and we can simulate and guess at missing data when working on more complex models


```{r}
png('geno-rf-est.png')
plot.rf(est.rf(qtl))
dev.off()
```

\clearpage

## Checking for QTLs

```{r results='hide', message=FALSE, warning=FALSE, fig.height = 10, fig.width = 7}

 for (col in colnames(qtl$pheno)){
 
   s1 <- scanone(qtl, method = "hk", pheno.col = col)
   s2 <- scanone(qtl, method = "em", pheno.col = col)
   s3 <- scanone(qtl, method = "mr", pheno.col = col)
   operm.hk <- scanone(qtl, method = "hk", pheno.col = col, model = "normal",
                       n.perm = 1000, verbose = FALSE)
 
   lod_threshold <- summary(operm.hk)
 
   perms <- scanone(qtl, pheno.col = col, n.perm = 1000, method = "hk")
 
   summary(s1, perms=perms, pvalues=T)
 
     if (max(s1$lod) >= 2.5 && max(s2$lod) > 2.5 && max(s3$lod) > 2.5) {
     kable(summary(s1))

	 png(sprintf('%s.png', col))
	 par(mfrow = (c(2, 1)))


     plot(s1, s2, s3, main = " ", col = c('green', 'blue', 'orange'), ity = 2)

	 title(sprintf("One-way scan QTL for: %s", col), outer=TRUE, line=-1)
     add.threshold(out=s1, perms = perms, col='red', ity=2, alpha=0.2)
     plot(perms)
     abline(v=quantile(perms,.95), col='red', ity=2)
 
	dev.off()
   }
 }
```



